

```{r}
library(readxl)
library(dplyr)
library(tidyr)
library(naniar)

library(httr)
library(jsonlite)

library(boxr)
library(openxlsx)

library(stringr)

library(haven)


```




```{r}

#Functions to read and write from Box
source('Read_Box_Functions.R')

```


Box API Tokens - Update these areas with token and desired output path
```{r}
# Generate token 
# Configuration Link: https://carene.app.box.com/developers/console/app/2431769/configuration

box_token <- 'mCC8LsDQgKrlMCQqovQInzcYOyW0K20Z'
auth_header <- add_headers(Authorization = paste("Bearer", box_token))


# Assign desired output path 
# Navigate to output folder and copy id in the URL (ex. https://carene.app.box.com/folder/342486719038)
baseline_processed_folder_id = '348165844236'
eyetracking_cleaned_folder_id = '342468940685' 

```



Read Outcomes Data
```{r}
# # Read in outcomes data
input_path = 'Freeview 2025/full USTBEST data files and code books/'
files = read_box_folder(input_path)$name

#Outcome and demographics file
# filename = 'USTBEST_Merged_12.3.24.csv'
filename = "USTREAT_ForML_RnRDemoUpdate.xlsx"

temp_file = read_box_file(input_path,filename)

df = read.xlsx(temp_file,na.strings = c("999","888",999,888)) 

#Keep unique IDs
df  =  distinct(df, PtID, .keep_all = TRUE)
```

Read Inclusions data
```{r}
## Read inclusions decisions list
inclusions_path = 'Freeview 2025/files from BEST folder/Data (from BEST_project on server)/Eyetracking Cleaned'

filename = 'inclusion_decisions_EventMarker_meta_data_9.29.25.xlsx'
temp_file = read_box_file(inclusions_path,filename)

## Read in excluded subjects list
subject_list = read_xlsx(temp_file)  



```


Identify subjects to include
```{r}

#Include only subjects with eye tracking data
df_select = df[(df$PtID %in% subject_list$subject),] 

```

Select variables
```{r}

# Define multiple replacements
replacements <- c(
  "PM" = "_1mo_",
  "TM" = "_3mo_",
  "LA" = "_LA_",
  "LT" = "_LT_",
  "CR" = "_CR_"
 )



```

Pull CSSRS items timepoint 1
```{r}

df_cssr_t1 <- df_select %>%
  filter(PtID %in% subject_list$subject) %>%
  select(
    PtID,
    # matches("CS01PMt1_R|CS03PMt1_R|CS05PMt1_R|CS07PMt1_R|CS08PMt1_R|CS12PMt1|CS14PMt1|CS15PMt1|CS23PMt1|CS28PMt1|CS30PMt1|CS32PMt1|CS34PMt1|CS39PMt1|CS40PMt1")) %>%
    matches("CS01PMt1_R|CS03PMt1_R|CS05PMt1_R|CS07PMt1_R|CS08PMt1_R|CS12PMt1|CS14PMt1|CS15PMt1")) %>%
  rename_with(~ str_replace_all(.x, replacements)) 



#If SI columsn are all zero, fill in zeroes for Suicide Behavior columns 
cond_cols   <- c('CS01_1mo_t1_R',
                 'CS03_1mo_t1_R',
                 'CS05_1mo_t1_R',
                 'CS07_1mo_t1_R',
                 'CS08_1mo_t1_R')

target_cols <- c('CS12_1mo_t1',
                 'CS14_1mo_t1',
                 'CS15_1mo_t1')


df_cssr_t1 <- df_cssr_t1 %>%
  mutate(across(
    all_of(target_cols),
    ~ if_else(rowSums(across(all_of(cond_cols))) == 0, 0, .)
  ))




```


```{r}

df_select <- df_select %>%
  filter(PtID %in% subject_list$subject) %>%
  select(
    PtID,
    PtCond,
    PtStatus,
    matches("DEMGB001$|DEMGB002|CS01|CS03|CS05|CS07|CS08|CS12|CS23|CS24|CS25|CS34|^S016|^S017|^S018"),
    -matches("LT"),
    CS24LTt1,
    CS25LTt1
  ) %>%
  replace_with_na(replace = list(
    DEMGB002 = c(999,888)))%>%
   mutate(across(matches("S01"), ~ na_if(.x, 888))) %>%
   mutate(across(matches("S01"), ~ na_if(.x, 999))) %>%
   mutate(across(c(DEMGB001,
                  DEMGB002),
                factor))%>%
  rename_with(~ str_replace_all(.x, replacements)) 





```

Outcomes at baseline
```{r}

df_select <- df_select %>%
  rowwise() %>%
  mutate(
    outcome_t1 = case_when(
      # Code suicide attempt behavior
      any(c_across(c(
        S018_CR_t1)) == 1) ~ "SA", # current episode SA (past 1 month)
      
      # Code suicide ideation behavior           
      any(c_across(c(
        CS01_1mo_t1, # wish to be dead (past 1 month)  
        CS03_1mo_t1, # nonspecific active SI (past 1 month) 
        CS05_1mo_t1, # active ideation w method w/o intent (past 1 month) 
        CS07_1mo_t1, # active ideation with intent w/o plan (past 1 month) 
        CS08_1mo_t1, #  active suicide ideation w plan and intent (past 1 month)
        S016_CR_t1)) == 1) ~ "SI", # current episode SI (past 1 month)
      
      # Code everything else 0 
      TRUE ~ "Control"
    )
  ) %>%
  ungroup()
  


```


Outcomes in 3 mo leading up to baseline
```{r}

df_select <- df_select %>%
  rowwise() %>%
  mutate(
    # Code suicide attempt behavior including 3 mo prior to baseline
    outcome_past3mo_t1 = case_when(
      any(c_across(c(
        CS23_3mo_t1, # actual attempts (past 3 month)
        CS24_3mo_t1, # passive and actual attempts (past 3 month)
        CS34_3mo_t1, # Suicidal behavior (past 3 month)
        S018_CR_t1)) == 1) ~ "SA", # current episode SA (past 1 month)
      
      # Code suicide ideation behavior
      any(c_across(c(
        CS01_1mo_t1, # wish to be dead (past 1 month)  
        CS03_1mo_t1, # nonspecific active SI (past 1 month) 
        CS05_1mo_t1, # active ideation w method w/o intent (past 1 month) 
        CS07_1mo_t1, # active ideation with intent w/o plan (past 1 month) 
        CS08_1mo_t1, #  active suicide ideation w plan and intent (past 1 month)
        S016_CR_t1)) == 1) ~ "SI", # current episode SI (past 1 month)
      
      # Code everything else 0   
      TRUE ~ 'Control' 
    )
  ) %>%
  ungroup()


```



Outcomes bt baseline and 6 mo follow up
```{r}
df_select <- df_select %>%
  rowwise() %>%
  mutate(
    outcome_t3 = case_when(
      
      # Code suicide attempt behavior since baseline if any of these variables = 1
      any(c_across(c(
        CS23_LA_t2, # actual attempts (since last appt)
        CS23_LA_t3, # actual attempts (since last appt) 
        
        CS24_LA_t2, # passive and actual attempts (since last appt)
        CS24_LA_t3, # passive and actual attempts (since last appt)
        
        CS34_LA_t2, #suicidal behavior (since last appt)
        CS34_LA_t3, # suicidal behavior (since last appt)
        
        S018_CR_t2,  # current episode SA (since last appt)
        S018_CR_t3)) == 1) ~ "SA",  # current episode SA (since last appt)
      
      # Code suicide ideation behavior since baseline           
      any(c_across(c(
        CS01_LA_t2, # wish to be dead (since last appt)
        CS01_LA_t3, # wish to be dead (since last appt)
        
        CS03_LA_t2, # nonspecific active SI (since last appt)
        CS03_LA_t3, # nonspecific active SI (since last appt)
        
        CS05_LA_t2, # active ideation w method w/o intent (since last appt)
        CS05_LA_t3, # active ideation w method w/o intent (since last appt)
        
        CS07_LA_t2, # active ideation with intent w/o plan (since last appt)
        CS07_LA_t3, # active ideation with intent w/o plan (since last appt)
        
        CS08_LA_t2, #  active suicide ideation w plan and intent (since last appt)
        CS08_LA_t3, #  active suicide ideation w plan and intent (since last appt)
        
        S016_CR_t2, # current episode SI (since last appt)
        S016_CR_t3)) == 1) ~ "SI", # current episode SI (since last appt)
      
      # Code everything else 0 
      TRUE ~ "Control"
    )
  ) %>%
  ungroup()



```




Outcomes bt baseline and 3 week follow up
```{r}
df_select <- df_select %>%
  rowwise() %>%
  mutate(
    outcome_t2 = case_when(
      
      # Code suicide attempt behavior since baseline if any of these variables = 1
      any(c_across(c(
        CS23_LA_t2, # actual attempts (since last appt)
        CS24_LA_t2, # passive and actual attempts (since last appt)
        CS34_LA_t2, #suicidal behavior (since last appt)
        S018_CR_t2)) == 1) ~ "SA",  # current episode SA (since last appt)
      
      # Code suicide ideation behavior since baseline           
      any(c_across(c(
        CS01_LA_t2, # wish to be dead (since last appt)
        CS03_LA_t2, # nonspecific active SI (since last appt)
        CS05_LA_t2, # active ideation w method w/o intent (since last appt)
        CS07_LA_t2, # active ideation with intent w/o plan (since last appt)
        CS08_LA_t2, #  active suicide ideation w plan and intent (since last appt)
        S016_CR_t2)) == 1) ~ "SI", # current episode SI (since last appt)
      
      # Code everything else 0 
      TRUE ~ "Control"
    )
  ) %>%
  ungroup()



```


Select columns with outcome data only
```{r}

df_outcomes = df_select %>%
  select(PtID, 
         PtCond, 
         DEMGB001,
         DEMGB002, 
         CS24_LT_t1, 
         CS25_LT_t1,
         outcome_t1,
         outcome_past3mo_t1,
         outcome_t2,
         outcome_t3) %>%
  rename('ParticipantName' = 'PtID')



```


Read all subjects' outcome group
```{r}

outcomes_path = 'Freeview 2025/files from BEST folder/Data (from BEST_project on server)/Eyetracking Cleaned'
filename = 'BEST clean merged 190419.xlsx'

#Takes a moment to connect to Box API
temp_file = read_box_file(outcomes_path,filename)

# Read in data
outcomes_original_df = read_xlsx(temp_file) %>% distinct(ParticipantName, .keep_all = TRUE) %>% select (ParticipantName,Group) 



```


Merge outcome group
```{r}
df_outcomes_6mo = merge(df_outcomes, outcomes_original_df,by = 'ParticipantName',all.y = TRUE) %>% 
  select(-PtCond) 

subject_include = subject_list %>% filter(`Include?` == 'Y')

df_outcomes_6mo = df_outcomes_6mo[(df_outcomes_6mo$ParticipantName %in% subject_include$subject),] 
  
```


```{r}

write_box_file(df_outcomes_6mo,eyetracking_cleaned_folder_id, 'outcomes_data_calculated_2.15.26.xlsx')
write_box_file(df_cssr_t1,eyetracking_cleaned_folder_id, 'cssrs_t1_2.7.26.xlsx')


```


Key
```{r}
# Y = 1 N = 2

#DEMOGB001 - Age




## ===== Baseline =====

# # SI variables
# S016CRt1 - current episode SI
# S017CRt1 - current episode plan
# S018CRt1 - current episode SA


# CS01PMt1 - wish to be dead past month  
# CS03PMt1 - nonspecific active SI past month 
# CS05PMt1 - active ideation w method w/o intent past month 
# CS07PMt1 - active ideation with intent w/o plan past month 
# CS08PMt1 - active suicide ideation w plan and intent past month 
# CS012PMt1 - most severe SI past month 
# CS013PMt1 - Descriptor past month 

# CS01TMt1 - wish to be dead past 3 month  
# CS03TMt1 - nonspecific active SI  past 3 month 
# CS05TMt1 - active ideation w method w/o intent  past 3 month 
# CS07TMt1 - active ideation with intent w/o plan  past 3 month 
# CS08TMt1 - active suicide ideation w plan and intent  past 3 month 
# CS012TMt1 - most severe SI  past 3 month 
# CS013TMt1 - Descriptor  past 3 month 

# # SA variables
#CS23PMt1 - actual attempts past month
#CS24PMt1 - passive and actual attempts past month

#CS23TMt1 - actual attempts past 3 month
#CS24TMt1 - passive and actual attempts past 3 month

#CS34TMt1 - suicidal behavior past 3 mo


## ===== 3 week follow up  =====

# # SI variables
# CS01LAt2 - wish to be dead since last appt  
# CS03LAt2 - nonspecific active SI since last appt 
# CS05LAt2 - active ideation w method w/o intent since last appt
# CS07LAt2 - active ideation with intent w/o plan since last appt 
# CS08LAt2 - active suicide ideation w plan and intent since last appt
# CS012LAt2 - most severe SI since last appt 
# CS013LAt2 - Descriptor since last appt


# CS01PMt2 - wish to be dead past month  
# CS03PMt2 - nonspecific active SI past month 
# CS05PMt2 - active ideation w method w/o intent past month 
# CS07PMt2 - active ideation with intent w/o plan past month 
# CS08PMt2 - active suicide ideation w plan and intent past month 
# CS012PMt2 - most severe SI past month 
# CS013PMt2 - Descriptor past month 

# CS01TMt2 - wish to be dead past 3 month  
# CS03TMt2 - nonspecific active SI  past 3 month 
# CS05TMt2 - active ideation w method w/o intent  past 3 month 
# CS07TMt2 - active ideation with intent w/o plan  past 3 month 
# CS08TMt2 - active suicide ideation w plan and intent  past 3 month 
# CS012TMt2 - most severe SI  past 3 month 
# CS013TMt2 - Descriptor  past 3 month 

# # SA variables
#CS23LAt2 - actual attempts since last appt
#CS24LAt2 - passive and actual attempts since last appt
#CS34LAt2 - suicidal behavior since last appt

#CS23PMt2 - actual attempts past 3 month
#CS24PMt2 - passive and actual attempts past 3 month

#CS23TMt2 - actual attempts past 3 month
#CS24TMt2 - passive and actual attempts past 3 month




## ===== 6 mo follow up  =====

# # SI variables
# CS01LAt3 - wish to be dead since last appt  
# CS03LAt3 - nonspecific active SI since last appt 
# CS05LAt3 - active ideation w method w/o intent since last appt
# CS07LAt3 - active ideation with intent w/o plan since last appt 
# CS08LAt3 - active suicide ideation w plan and intent since last appt
# CS012LAt3 - most severe SI since last appt 
# CS013LAt3 - Descriptor since last appt


# CS01PMt3 - wish to be dead past month  
# CS03PMt3 - nonspecific active SI past month 
# CS05PMt3 - active ideation w method w/o intent past month 
# CS07PMt3 - active ideation with intent w/o plan past month 
# CS08PMt3 - active suicide ideation w plan and intent past month 
# CS012PMt3 - most severe SI past month 
# CS013PMt3 - Descriptor past month 

# CS01TMt3 - wish to be dead past 3 month  
# CS03TMt3 - nonspecific active SI  past 3 month 
# CS05TMt3 - active ideation w method w/o intent  past 3 month 
# CS07TMt3 - active ideation with intent w/o plan  past 3 month 
# CS08TMt3 - active suicide ideation w plan and intent  past 3 month 
# CS012TMt3 - most severe SI  past 3 month 
# CS013TMt3 - Descriptor  past 3 month 

# # SA variables
#CS23LAt3 - actual attempts since last appt
#CS24LAt3 - passive and actual attempts since last appt
#CS34LAt3 - suicidal behavior since last appt

#CS23PMt3 - actual attempts past 3 month
#CS24PMt3 - passive and actual attempts past 3 month

#CS23TMt3 - actual attempts past 3 month
#CS24TMt3 - passive and actual attempts past 3 month

```
